Mining of Keystroke and Mouse Dynamics to Increase the Engagement of Students with Programming Assignments

### 2018-04-21 paper.tex
Table correction
Review changes in commit ed2faa3

As part of the data mining process a canonical genetic algorithm was used for feature
selection with the parameters used shown in Table \ref{tab_ga}. These
parameters were set heuristically, and were the same for selecting the
features of all classification algorithms. % Mario check this - JJ
In the end, the subset for the frustration classifier includes only 11 features, and 
the subset for the boredom classifier consists of only 13 features.

@@

      Algorithm & Parameters \\
      \hline
    \end{tabular}
  \end{table}

>>>>

As part of the data mining process a canonical genetic algorithm was used for feature
selection with the parameters used shown in Table \ref{tab_ga}. These
parameters were set heuristically and were the same for selecting the
features of all classification algorithms. The population size was changed
mainly because the feature vector is real-valued and is more computationally demanding.  
% Mario check this - JJ
% OK, added another sentence - Mario 
In the end, the subset for the frustration classifier includes only 11 features, and 
the subset for the boredom classifier consists of only 13 features.

@@

      Algorithm & Parameters \\
      \hline
    \end{tabular}
  \end{table*}
